### 2022-07-21 paper/localpsf.tex
consistent ordering of plots and tables (psf, reg, none)
added m1_psf, m3_psf, m4_psf, mfinal_psf Newton iterates, incorporated them into the tex file, also added images with ColorBars so that we do not need to have 6 includegraphics calls for the ice mountain, true velocity and true parameter plots. I need to adjust these so that the colorbar is the same size on all three but this will require redoing the paraview plots and I would like to defer that effort for a later date

\begin{figure}[H]
	\begin{center}
		\begin{tabular}[c]{c c c}
			%\includegraphics[scale=.15]{recoveredPressure.png} &
			%\includegraphics[scale=.15]{truePressure.png} &
			%\includegraphics[scale=.18]{pressureColorBar.png} \\
			\includegraphics[scale=.15]{recoveredVelocity_glyphs.png} &
			\includegraphics[scale=.15]{trueVelocity_glyphs.png} &
			\includegraphics[scale=.18]{velocityColorBar.png} \\
			\includegraphics[scale=.15]{recoveredVelocity_noglyphs.png} &
			\includegraphics[scale=.15]{trueVelocity_noglyphs.png} &
			\includegraphics[scale=.18]{velocityColorBar.png}
		\end{tabular}
		\caption{Reconstructed (left column) and true (right column) pressure (top row) and velocity fields (middle and bottom rows).}
	\end{center}
\end{figure}

\begin{table}[H]
	\begin{center}
		\begingroup
		\setlength{\tabcolsep}{8pt}
		\renewcommand{\arraystretch}{1.25}
		\begin{tabular}{c| c c c | c c c | c c c}
			&  \multicolumn{3}{|c|}{PSF} & \multicolumn{3}{|c|}{REG} & \multicolumn{3}{|c}{NONE} \\
			\hline
			Iter & 
			\#CG & \#Stokes & $||g||$ & 
			\#CG & \#Stokes & $||g||$ & 
			\#CG & \#Stokes & $||g||$ \\
			\verb~0~ &
			\verb~1~ & \verb~4~ & \verb~1.95e+7~ &
			\verb~1~ & \verb~4~ & \verb~1.95e+7~ &
			\verb~1~ & \verb~4~ & \verb~1.95e+7~ \\
			\verb~1~ &
			\verb~2~ & \verb~6~ & \verb~5.76e+6~ &
			\verb~2~ & \verb~6~ & \verb~7.90e+6~ &
			\verb~2~ & \verb~6~ & \verb~5.76e+6~ \\
			\verb~2~ &
			\verb~4~ & \verb~10~ & \verb~2.36e+6~ &
			\verb~5~ & \verb~12~ & \verb~3.87e+6~ &
			\verb~4~ & \verb~10~ & \verb~2.36e+6~ \\
			\verb~3~ &
			\verb~2~ & \verb~6+22~ & \verb~5.79e+5~ &
			\verb~13~ & \verb~28~ & \verb~1.62e+6~ &
			\verb~13~ & \verb~28~ & \verb~5.79e+5~ \\
			\verb~4~ &
			\verb~5~ & \verb~12~ & \verb~5.61e+4~ &
			\verb~42~ & \verb~86~ & \verb~4.78e+5~ &
			\verb~33~ & \verb~68~ & \verb~9.05e+4~ \\
			\verb~5~ &
			\verb~10~ & \verb~22~ & \verb~3.45e+3~ &
			\verb~84~ & \verb~170~ & \verb~7.72e+4~ &
			\verb~57~ & \verb~116~ & \verb~6.21e+3~ \\
			\verb~6~ &
			\verb~14~ & \verb~30~ & \verb~2.66e+1~ &
			\verb~125~ & \verb~252~ & \verb~5.04e+3~ &
			\verb~76~ & \verb~154~ & \verb~1.05e+2~ \\
			\verb~7~ &
			\verb~0~ & \verb~2~ & \verb~4.09e-2~ &
			\verb~194~ & \verb~390~ & \verb~7.91e+1~ &
			\verb~117~ & \verb~236~ & \verb~2.29e-1~ \\
			\verb~8~ & 
			\verb~---~ & \verb~---~ & \verb~---~ &
			\verb~0~ & \verb~2~ & \verb~1.60e-1~ &
			\verb~0~ & \verb~2~ & \verb~4.08e-2~ \\
			\hline
			Total & 
			\verb~38~ & \verb~114~ & \verb~---~ &
			\verb~466~ & \verb~950~ & \verb~---~ &
			\verb~303~ & \verb~624~ & \verb~---~ \\
		\end{tabular}
		\endgroup
	\end{center}
\end{table}

\begin{figure}[H]
\begin{subfigure}{0.49\textwidth}
	\centering
	\begin{tikzpicture}[baseline, trim axis right]
	\begin{axis}[width=0.99\linewidth, height=1.0\linewidth,
	ymode=log,
	ymin=1e-11,
	ymax=2,
	xmax=750,
	axis x line*=bottom,
	axis y line*=left,
	xtick={0, 200, 400, 600},
	xlabel={CG iteration},
	ylabel={Relative residual norm},
	title={CG convergence},
	legend style={at={(1.1,1)},anchor=north east},
	%legend pos=north east,
	legend style={font=\small}
	]
	\addlegendentry{None}
	\addplot[dash dot, line width=0.5mm] table {cg_relres_none.dat};
	\addlegendentry{Reg}
	\addplot[dotted, line width=0.5mm] table {cg_relres_reg.dat};
	\addlegendentry{PSF (1)}
	\addplot[blue, line width=0.5mm] table {cg_relres_p1.dat};
	\addlegendentry{PSF (5)}
	\addplot[red, line width=0.5mm] table {cg_relres_p5.dat};
	\addlegendentry{PSF (25)}
	\addplot[purple, line width=0.5mm] table {cg_relres_p25.dat};
	\end{axis}
	\end{tikzpicture}
\end{subfigure}
	\begin{subfigure}{0.49\textwidth}
		\centering
		\begin{tikzpicture}[baseline, trim axis right]
		\begin{axis}[width=0.99\linewidth, height=1.0\linewidth,
		xmode=log,
		ymode=log,
		xlabel={$\gamma$, regularization parameter},
		ylabel={\# of CG iterations},
		axis y line*=right,
		axis x line*=bottom,
		ylabel near ticks, yticklabel pos=right,
		%ylabel near ticks, ylabel shift={-6pt},
		%legend pos=north east,
		title={Regularization robustness}
		%title={CG iterations to achieve $||H x-b||/||b||<10^{-6}$}
		]
		%\addlegendentry{None}
		\addplot[dash dot, line width=0.5mm] table[x=gamma, y=none] {CGitsvsGamma.dat};
		%\addlegendentry{REG}
		\addplot[dotted, line width=0.5mm] table[x=gamma, y=reg] {CGitsvsGamma.dat};
		%\addlegendentry{PSF (1)}
		\addplot[blue, line width=0.5mm] table[x=gamma, y=psf1] {CGitsvsGamma.dat};
		%\addlegendentry{PSF (5)}
		\addplot[red, line width=0.5mm] table[x=gamma, y=psf5] {CGitsvsGamma.dat};
		%\addlegendentry{PSF (25)}
		\addplot[purple, line width=0.5mm] table[x=gamma, y=psf25] {CGitsvsGamma.dat};
		\end{axis}
		\end{tikzpicture}
	\end{subfigure}
\end{figure}

\begin{figure}[H]
	\begin{subfigure}{0.59\textwidth}
	\begin{center}
		\begin{tikzpicture}[baseline, trim axis right]
		\begin{axis}[width=0.99\linewidth, height=0.8\linewidth,
		ymode=log,
		xmin=-50,
		xmax=1450,
		ymax=1.e4,
		xlabel={$k$, generalized eigenvalue \#},
		ylabel={$\lambda_{k}$},
		xtick={0, 300, 600, 900, 1200},
		%legend pos=north east,
		legend style={font=\small},
		ylabel near ticks, ylabel shift={-6pt},
		axis x line*=bottom,
		axis y line*=left,
		legend style={at={(0.95,1)},anchor=north east},
		title={Generalized eigenvalues, $Hu_{k}=\lambda_{k}Pu_{k}$}
		]
		\addlegendentry{REG}
		\addplot[dotted, line width=0.5mm] table[x=k, y=reg] {generalizedEigenvalues.dat};
		\addlegendentry{PSF (1)}
		\addplot[blue, line width=0.5mm] table[x=k, y=psf1] {generalizedEigenvalues.dat};
		\addlegendentry{PSF (5)}
		\addplot[red, line width=0.5mm] table[x=k, y=psf5] {generalizedEigenvalues.dat};
		\addlegendentry{PSF (25)}
		\addplot[purple, line width=0.5mm] table[x=k, y=psf25] {generalizedEigenvalues.dat};
		\end{axis}
		\end{tikzpicture}
	\end{center}
\end{subfigure}
\begin{subfigure}{0.39\textwidth}
		\begin{center}
		\begingroup
		\setlength{\tabcolsep}{4pt}
		\renewcommand{\arraystretch}{1.25}
		\begin{tabular}{c| c c}
			& $\kappa(P^{-1}H)$ &	$\kappa(P^{-1}H_{\text{gn}})$ \\
			\hline 
			REG        & \verb~7.0e+3~ & \verb~7.0e+3~ \\
			NONE       & \verb~8.7e+2~ & \verb~9.2e+2~ \\
			PSF $(1)$  & \verb~1.8e+1~ & \verb~1.8e+1~ \\
			PSF $(5)$  & \verb~1.4e+1~ & \verb~1.4e+1~ \\
			PSF $(25)$ & \verb~1.0e+1~ & \verb~1.1e+1~
		\end{tabular}
		\endgroup
	\end{center}
\end{subfigure}
\end{figure}

>>>>

\begin{figure}[H]
	\begin{subfigure}{0.275\textwidth}
    \includegraphics[scale=0.10]{meshHeight_view0_edges_withColorBar.png}	
    \end{subfigure}
    \begin{subfigure}{0.275\textwidth}
    \includegraphics[scale=0.10]{trueVelocity_glyphs_withColorBar.png}
    \end{subfigure}
    \begin{subfigure}{0.275\textwidth}
    \includegraphics[scale=0.135]{mtrue_withColorBar.png}
    \end{subfigure}
\end{figure}

\begin{table}[H]
	\begin{center}
		\begingroup
		\setlength{\tabcolsep}{4pt}
		\renewcommand{\arraystretch}{1.25}
		\begin{tabular}{c| c c c | c c c | c c c}
			&  \multicolumn{3}{|c|}{PSF} & \multicolumn{3}{|c|}{REG} & \multicolumn{3}{|c}{NONE} \\
			\hline
			Iter & 
			\#CG & \#Stokes & $||g||$ & 
			\#CG & \#Stokes & $||g||$ & 
			\#CG & \#Stokes & $||g||$ \\
			\verb~0~ &
			\verb~1~ & \verb~4~ & \verb~1.95e+7~ &
			\verb~1~ & \verb~4~ & \verb~1.95e+7~ &
			\verb~1~ & \verb~4~ & \verb~1.95e+7~ \\
			\verb~1~ &
			\verb~2~ & \verb~6~ & \verb~5.76e+6~ &
			\verb~2~ & \verb~6~ & \verb~7.90e+6~ &
			\verb~2~ & \verb~6~ & \verb~5.76e+6~ \\
			\verb~2~ &
			\verb~4~ & \verb~10~ & \verb~2.36e+6~ &
			\verb~5~ & \verb~12~ & \verb~3.87e+6~ &
			\verb~4~ & \verb~10~ & \verb~2.36e+6~ \\
			\verb~3~ &
			\verb~2~ & \verb~6+22~ & \verb~5.79e+5~ &
			\verb~13~ & \verb~28~ & \verb~1.62e+6~ &
			\verb~13~ & \verb~28~ & \verb~5.79e+5~ \\
			\verb~4~ &
			\verb~5~ & \verb~12~ & \verb~5.61e+4~ &
			\verb~42~ & \verb~86~ & \verb~4.78e+5~ &
			\verb~33~ & \verb~68~ & \verb~9.05e+4~ \\
			\verb~5~ &
			\verb~10~ & \verb~22~ & \verb~3.45e+3~ &
			\verb~84~ & \verb~170~ & \verb~7.72e+4~ &
			\verb~57~ & \verb~116~ & \verb~6.21e+3~ \\
			\verb~6~ &
			\verb~14~ & \verb~30~ & \verb~2.66e+1~ &
			\verb~125~ & \verb~252~ & \verb~5.04e+3~ &
			\verb~76~ & \verb~154~ & \verb~1.05e+2~ \\
			\verb~7~ &
			\verb~0~ & \verb~2~ & \verb~4.09e-2~ &
			\verb~194~ & \verb~390~ & \verb~7.91e+1~ &
			\verb~117~ & \verb~236~ & \verb~2.29e-1~ \\
			\verb~8~ & 
			\verb~---~ & \verb~---~ & \verb~---~ &
			\verb~0~ & \verb~2~ & \verb~1.60e-1~ &
			\verb~0~ & \verb~2~ & \verb~4.08e-2~ \\
			\hline
			Total & 
			\verb~38~ & \verb~114~ & \verb~---~ &
			\verb~466~ & \verb~950~ & \verb~---~ &
			\verb~303~ & \verb~624~ & \verb~---~ \\
		\end{tabular}
		\endgroup
	\end{center}
\end{table}

\begin{figure}[H]
	\begin{subfigure}{0.225\textwidth}
		\includegraphics[scale=0.08]{m1_psf.png}	
	\end{subfigure}
	\begin{subfigure}{0.225\textwidth}
		\includegraphics[scale=0.08]{m3_psf.png}
	\end{subfigure}
	\begin{subfigure}{0.225\textwidth}
		\includegraphics[scale=0.08]{m4_psf.png}
	\end{subfigure}
	\begin{subfigure}{0.225\textwidth}
	\includegraphics[scale=0.08]{m6_psf.png}
\end{subfigure}
\begin{subfigure}{0.05\textwidth}
	\includegraphics[scale=0.1]{mColorBar.png}
\end{subfigure}
\caption{The parameter after $1$ (left), $3$ (second from left), $4$ (third from left) Newton iterates and the final Newton iterate (right).} 
\end{figure}

\begin{figure}[H]
\begin{subfigure}{0.49\textwidth}
	\centering
	\begin{tikzpicture}[baseline, trim axis right]
	\begin{axis}[width=0.99\linewidth, height=1.0\linewidth,
	ymode=log,
	ymin=1e-11,
	ymax=2,
	xmax=750,
	axis x line*=bottom,
	axis y line*=left,
	xtick={0, 200, 400, 600},
	xlabel={CG iteration},
	ylabel={Relative residual norm},
	title={CG convergence},
	legend style={at={(1.1,1)},anchor=north east},
	%legend pos=north east,
	legend style={font=\small}
	]
	\addlegendentry{PSF (1)}
    \addplot[blue, line width=0.5mm] table {cg_relres_p1.dat};
    \addlegendentry{PSF (5)}
    \addplot[red, line width=0.5mm] table {cg_relres_p5.dat};
    \addlegendentry{PSF (25)}
    \addplot[purple, line width=0.5mm] table {cg_relres_p25.dat};
	\addlegendentry{Reg}
    \addplot[dotted, line width=0.5mm] table {cg_relres_reg.dat};
	\addlegendentry{None}
	\addplot[dash dot, line width=0.5mm] table {cg_relres_none.dat};
	\end{axis}
	\end{tikzpicture}
\end{subfigure}
	\begin{subfigure}{0.49\textwidth}
		\centering
		\begin{tikzpicture}[baseline, trim axis right]
		\begin{axis}[width=0.99\linewidth, height=1.0\linewidth,
		xmode=log,
		ymode=log,
		xlabel={$\gamma$, regularization parameter},
		ylabel={\# of CG iterations},
		axis y line*=right,
		axis x line*=bottom,
		ylabel near ticks, yticklabel pos=right,
		%ylabel near ticks, ylabel shift={-6pt},
		%legend pos=north east,
		title={Regularization robustness}
		%title={CG iterations to achieve $||H x-b||/||b||<10^{-6}$}
		]
		%\addlegendentry{None}
		\addplot[dash dot, line width=0.5mm] table[x=gamma, y=none] {CGitsvsGamma.dat};
		%\addlegendentry{REG}
		\addplot[dotted, line width=0.5mm] table[x=gamma, y=reg] {CGitsvsGamma.dat};
		%\addlegendentry{PSF (1)}
        \addplot[blue, line width=0.5mm] table[x=gamma, y=psf1] {CGitsvsGamma.dat};
        %\addlegendentry{PSF (5)}
        \addplot[red, line width=0.5mm] table[x=gamma, y=psf5] {CGitsvsGamma.dat};
        %\addlegendentry{PSF (25)}
        \addplot[purple, line width=0.5mm] table[x=gamma, y=psf25] {CGitsvsGamma.dat};
		\end{axis}
		\end{tikzpicture}
	\end{subfigure}
\end{figure}

\begin{figure}[H]
	\begin{subfigure}{0.59\textwidth}
	\begin{center}
		\begin{tikzpicture}[baseline, trim axis right]
		\begin{axis}[width=0.99\linewidth, height=0.8\linewidth,
		ymode=log,
		xmin=-50,
		xmax=1450,
		ymax=1.e4,
		xlabel={$k$, generalized eigenvalue \#},
		ylabel={$\lambda_{k}$},
		xtick={0, 300, 600, 900, 1200},
		%legend pos=north east,
		legend style={font=\small},
		ylabel near ticks, ylabel shift={-6pt},
		axis x line*=bottom,
		axis y line*=left,
		legend style={at={(0.95,1)},anchor=north east},
		title={Generalized eigenvalues, $Hu_{k}=\lambda_{k}Pu_{k}$}
		]
		\addlegendentry{PSF (1)}
        \addplot[blue, line width=0.5mm] table[x=k, y=psf1] {generalizedEigenvalues.dat};
        \addlegendentry{PSF (5)}
        \addplot[red, line width=0.5mm] table[x=k, y=psf5] {generalizedEigenvalues.dat};
        \addlegendentry{PSF (25)}
        \addplot[purple, line width=0.5mm] table[x=k, y=psf25] {generalizedEigenvalues.dat};
		\addlegendentry{REG}
		\addplot[dotted, line width=0.5mm] table[x=k, y=reg] {generalizedEigenvalues.dat};
		\end{axis}
		\end{tikzpicture}
	\end{center}
\end{subfigure}
\begin{subfigure}{0.39\textwidth}
		\begin{center}
		\begingroup
		\setlength{\tabcolsep}{4pt}
		\renewcommand{\arraystretch}{1.25}
		\begin{tabular}{c| c c}
			& $\kappa(P^{-1}H)$ &	$\kappa(P^{-1}H_{\text{gn}})$ \\
			\hline 
			PSF $(1)$  & \verb~1.8e+1~ & \verb~1.8e+1~ \\
            PSF $(5)$  & \verb~1.4e+1~ & \verb~1.4e+1~ \\
            PSF $(25)$ & \verb~1.0e+1~ & \verb~1.1e+1~ \\
			REG        & \verb~7.0e+3~ & \verb~7.0e+3~ \\
			NONE       & \verb~8.7e+2~ & \verb~9.2e+2~ 
		\end{tabular}
		\endgroup
	\end{center}
\end{subfigure}
\end{figure}
